Multispecies survey specifications

### 2020-11-05 msSurveysTest.Rmd
update survey configs and rerun

survObsBiom <- read_savedsurvs(d.name, 'survB')
age_comp_data <- read_savedsurvs(d.name, 'survAge')
len_comp_data <- read_savedsurvs(d.name, 'survLen')
wtage <- read_savedsurvs(d.name, 'survWtage')
annage_comp_data <- read_savedsurvs(d.name, 'survAnnAge')
annage_wtage <- read_savedsurvs(d.name, 'survAnnWtage')

@@

catchbio_ss <- readRDS(file.path(d.name, paste0(scenario.name, "fishCatch.rds")))
catchbio_ss <- catchbio_ss[[1]] #in same time unit as surveys

fish_age_comp <- readRDS(file.path(d.name, paste0(scenario.name, "fishObsAgeComp.rds")))
fish_age_comp <- fish_age_comp[[1]]

@@

fish_len_comp_data <- readRDS(file.path(d.name, paste0(scenario.name, "fishObsLenComp.rds")))

@@

fishwtage <- readRDS(file.path(d.name, paste0(scenario.name, "fishObsWtAtAge.rds")))
fishwtage <- fishwtage[[1]] #need to change time units?

fish_annage_comp <- readRDS(file.path(d.name, paste0(scenario.name, "fishObsFullAgeComp.rds")))
fish_annage_comp <- fish_annage_comp[[1]]

@@

fish_annage_wtage <- readRDS(file.path(d.name, paste0(scenario.name, "fishObsFullWtAtAge.rds")))
fish_annage_wtage <- fish_annage_wtage[[1]] #need to change time units?

@@

>>>>

# add this paste0(d.name, "/mscensus1") and add option to name save directory in wrappers
survObsBiom <- read_savedsurvs(paste0(d.name, "/mscensus1"), 'survB')
age_comp_data <- read_savedsurvs(paste0(d.name, "/mscensus1"), 'survAge')
len_comp_data <- read_savedsurvs(paste0(d.name, "/mscensus1"), 'survLen')
wtage <- read_savedsurvs(paste0(d.name, "/mscensus1"), 'survWtage')
annage_comp_data <- read_savedsurvs(paste0(d.name, "/mscensus1"), 'survAnnAge')
annage_wtage <- read_savedsurvs(paste0(d.name, "/mscensus1"), 'survAnnWtage')

@@

catchbio_ss <- readRDS(file.path(paste0(d.name, "/mscensus1"), paste0(scenario.name, "fishCatch.rds")))
catchbio_ss <- catchbio_ss[[1]] #in same time unit as surveys

fish_age_comp <- readRDS(file.path(paste0(d.name, "/mscensus1"), paste0(scenario.name, "fishObsAgeComp.rds")))
fish_age_comp <- fish_age_comp[[1]]

@@

fish_len_comp_data <- readRDS(file.path(paste0(d.name, "/mscensus1"), paste0(scenario.name, "fishObsLenComp.rds")))

@@

fishwtage <- readRDS(file.path(paste0(d.name, "/mscensus1"), paste0(scenario.name, "fishObsWtAtAge.rds")))
fishwtage <- fishwtage[[1]] #need to change time units?

fish_annage_comp <- readRDS(file.path(paste0(d.name, "/mscensus1"), paste0(scenario.name, "fishObsFullAgeComp.rds")))
fish_annage_comp <- fish_annage_comp[[1]]

@@

fish_annage_wtage <- readRDS(file.path(paste0(d.name, "/mscensus1"), paste0(scenario.name, "fishObsFullWtAtAge.rds")))
fish_annage_wtage <- fish_annage_wtage[[1]] #need to change time units?

@@

NOTE! Need to have selectivities defined *both* for annual ages and for age classes. Worked in census because flat selectivity was defined for full set of annual ages and it just didn't use past age 10 for age class output. They were all 1 anyway so it didnt matter. The updated survey config file first specifies selectivity by true age and then backs out an approximate equivalent for age classes. We will use true age classes for the real datasets but wanted to check both outputs here. `om_comps()` has now changed to take `survselex.agecl` as input to the age class comps and survselex as input to the full comps.

Both `om_index()` and `om_comps()` wrappers now name fishery output based on a `fishery.name` in the fishery config file.
